---
position: "MRCP PhD MBBS MPhys"
#address: "20 Castleton Road, London, E17 4AR"
#phone: "+44(0)7889192790"
profilepic: "ProfilePic.jpg"
#email: "a.pennycuick@ucl.ac.uk"
twitter: "adampennycuick"
linkedin: "adam-pennycuick-68401737"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
# Requirements:
# biocManager::install('vitae')
# .Renviron file containing this line:
#   ORCID_TOKEN="XXXX"
# where the token comes from running
# library(rorcid)
# orcid_auth()

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

# My orcid ID:
oid <- "0000-0001-5836-0250"
```

```{r}
#Beware of Latex and the latex packages needed for compiling. See https://yihui.org/tinytex/r/#debugging if you get any errors related to *.tex compiling 
```

---
name: "`r rorcid::orcid_id(oid)[[oid]]$name$'given-names'$value`"
surname: "`r rorcid::orcid_id(oid)[[oid]]$name$'family-name'$value`"
aboutme: "`r rorcid::orcid_bio(orcid = oid)[[oid]]$content`"
---

# Education

```{r}
library(rorcid)
library(dplyr)
my_ed <- do.call("bind_rows",
  rorcid::orcid_educations(oid)[[oid]]$`affiliation-group`$summaries
)
my_ed %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
# library(tibble)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#   detailed_entries(Degree, Year, Institution, Where)
```

# Work experience

```{r}
my_exp <- do.call("bind_rows",
  rorcid::orcid_employments(oid)[[oid]]$`affiliation-group`$summaries
)

# Change NA to "Present"
my_exp$`employment-summary.end-date.year.value`[which(is.na(my_exp$`employment-summary.end-date.year.value`))] <- 'now'

#For the my_exp variable below: if there is no end date on your recent employment, replace `employment-summary.end-date.year.value` with `employment-summary.end-date`. 
my_exp %>%
  detailed_entries(
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    with = `employment-summary.organization.name`,
    where = glue::glue("{`employment-summary.organization.address.city`}")
  )

#tribble(
#  ~ Experience, ~ Year, ~ Institution, ~ Details,
#  "Current Job Title", "Years of Employment", "Organization", #"Job Description",
#  "Previous Job Title", "Years of Employment", "Organization", #"Job Description",
  
#) %>% 
#  detailed_entries(Details, Year, Experience, Institution)
```

# Grants Awarded:

  * **Parallelised Cancer Therapy based on Copy Number Targeting (PI)**. Academy of Medical Sciences. 2023-2024, £20,000.
  * **Epi-ASCENT: The epigenetic landscape of screen-detected lung cancers (Co-I)**. Cancer Research UK. 2022-2025, £194,000.
  * **ELIMINATE: Reinterpreting the ‘field of injury’ through understanding cellular level damage and dynamics and consequences for the Prediction, Prevention and Early Detection, of lung cancer (Co-I)**. Cancer Research UK. 2020-2025, £2.5m
* **ASCENT: Analysis of screen-detected lung cancer genomic traits (Co-I)**. Cancer Research UK. 2019-2022, £600,000
* **Wellcome Trust/UCL PhD Training Fellowship**: Bioinformatic analysis of early lung cancer pathogenesis. 2017-2021. £270,000.
* **Oslr medical bedside teaching platform**. 2019. InnovateUK. £70,000.

# Supervision:

* Primary PhD supervisor for Hugh Selway, UCL 2021-present.
* Secondary PhD supervisor for Lukas Kalinke (clinical fellow at UCL 2019-2022); Ryan Chuen (UCL 2022-present); Kate Davies (UCL 2022-present); James Lam (UCL 2023-present).
* Primary supervisor for Ayu Syarif, MSc in Precision Oncology, UCL 2020.
* Supervised MRC-DTP project for Kate Fodder, UCL 2021.
* Personal tutor for UCL students 2022-present.

# Teaching and Leadership:

* **Founder and CEO of Oslr Ltd.**, a platform connecting medical students with doctors willing to teach. Supporters include Health Education England, the BMJ, Jisc, King’s College London, Guy’s and St Thomas’ NHS Foundation Trust. Our platform has won innovation awards and is live across multiple hospital sites. £230,000 funding has been raised to date through a combination of grants and private investment, including Innovate UK funding. I lead a team of 5 people.
* **Leadership Fellow** Society of Leadership Fellows, St Georges House, Windsor Castle. 2023-present.
* **Regular bedside teaching experience** throughout clinical training, including leading the Denmark Hill Teaching Group at King's College Hospital and delivering lecture courses. Taught entrepreneurship to medical students.
* Non-medical teaching experience including maths and science tutoring at age 10-16, and teaching English as a foreign language at Moscow State University.

<!-- # Skills -->
<!-- These are some of the skills and knowledge I aquired during my training, education and courses -->

<!--   * **First overarching skillname**:   -->
<!--       List the details, including software, techniques, etc. -->
<!--   * **Second overarching skillname**:   -->
<!--       List the details, including software, techniques, etc. -->
<!--   * **Other informatic tools**:   -->
<!--       Microsoft Office; Google Suite; GraphPad Prism; LaTeX; Git; HTML & CSS. -->
<!--   * **Public speaking**:   -->
<!--       I  have attended and presented my scientific work in several national and international conferences, both orally and in poster format. -->
      
***
      
# Key Selected Publications

```{r}
# Present two separate lists of 'selected' and 'other' publications

selected <- c(
  "Immune Surveillance in Clinical Regression of Preinvasive Squamous Cell Lung Cancer",
  "Deciphering the genomic, epigenomic, and transcriptomic landscapes of pre-invasive lung cancer lesions"
)

# Label co-first papers:
cofirst <- c(
  "Deciphering the genomic, epigenomic, and transcriptomic landscapes of pre-invasive lung cancer lesions",
  "Molecular Characterization of Acute Cellular Rejection Occurring During Intentional Immunosuppression Withdrawal in Liver Transplantation."
)

library(rorcid)
library(tidyverse)
out <- works(orcid_id(oid)) 

# Need to get authors separately:
y <- orcid_works(oid, put_code = out$`put-code`)
y <- y[[1]]$works
y <- y[match(out$`put-code`, y$`work.put-code`),]
out$authors <- sapply(out$`put-code`, function(x) {
  z <- y[which(y$`work.put-code` == x),]
  auths <- z$work.contributors.contributor[[1]]$`credit-name.value`
  # Limit authors to max(5, my position), if longer use et. al
  mypos <- grep('Pennycuick', auths)
  maxlen <- max(6, mypos)
  if(length(auths) > maxlen) {
    auths <- c(auths[1:maxlen], 'et. al')
  }

  a <- paste(auths, collapse = ', ')
  
  if(z$work.title.title.value %in% cofirst) {
    a <- paste("(Co-first author)", a)
  }
  
  a
})



# Bug fixes
out$title.title.value <- gsub('<i>', '', out$title.title.value)
out$title.title.value <- gsub('</i>', '', out$title.title.value)

papers <- tibble(
  Journal = out$`journal-title.value`,
  Title = out$title.title.value,
  Year = out$`publication-date.year.value`,
  DOI = out$url.value,
  Authors = gsub('Adam Pennycuick', 'Adam Pennycuick', out$authors, fixed = T)
) 

papers %>%
  filter(Title %in% selected) %>%
  detailed_entries(
    Title,
    Year,
    Authors,
    Journal,
    # Year, 
    DOI
)

```

# Other Publications

```{r}
papers %>%
  filter(!(Title %in% selected)) %>%
  detailed_entries(
    Title,
    Year,
    Authors,
    Journal,
    # Year, 
    DOI
)
```